\plaintitle

### 2016-08-16 drafts/labor/cases.tex
small notes

\subsection{What are the limits of crowdsourcing?}
Research in crowdsourcing has spent the better part of a decade
exploring ways of growing the limits of crowdsourcing and
finding the boundaries of crowd work and microtasks;
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes, and
  repeating the process
\cite{bernsteinSoylent}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  \item \nameref{sec:decomposition},
  \item \nameref{sec:workAbstraction}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing,
% As we'll discuss these dimensions,
discussing the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

@@

\subsubsection{Decomposition (how high can we stack the salami?)}\label{sec:decomposition}
Crowdsourcing has explored the decomposition of work for the better part of a decade;
\citeauthor{crowdForgeKittur} specifically
drive at this goal by addressing the possibility of
crowdsourcing complex work
\cite{crowdForgeKittur}.
\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work is susceptible to frequent interruptions
\cite{cheng2015break}.

>>>>

% let's do topic sentences!
\subsection{What are the limits of crowdsourcing?}
Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing and
find the boundaries of crowd work and microtasks;
this has largely involved
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes, and
  repeating the process
\cite{bernsteinSoylent}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  % \item \cref*{sec:decomposition},
  \item \lowercase{\nameref{sec:decomposition}},
  \item \nameref{sec:workAbstraction}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing,
% As we'll discuss these dimensions,
discussing the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

@@

\subsubsection{Achieving complexity}\label{sec:decomposition}
Crowdsourcing has explored the decomposition of work for the better part of a decade;
\citeauthor{crowdForgeKittur} specifically
drive at this goal by addressing the possibility of
crowdsourcing complex work
\cite{crowdForgeKittur}.
\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work is susceptible to frequent interruptions
\cite{cheng2015break}.
